---
title: "Active Maintenance Report: coppock_2019a"
subtitle: "Coppock (2019, PSRM): Generalizing from Survey Experiments Conducted on Mechanical Turk"
format:
  gfm:
    output-file: README.md
    toc: true
  pdf:
    output-file: coppock_2019a_report.pdf
    toc: true
    toc-depth: 2
    number-sections: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)

here::i_am("README.qmd")

# The errata spine, defined once in errata.qmd and written out by it. This report reads it
# rather than keeping its own count, so the two cannot disagree about how many entries there
# are.
spine <- read_csv(here("errata_entries.csv"), show_col_types = FALSE)
n_errata_word <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
                   "ten", "eleven", "twelve")[nrow(spine)]

# kableExtra styling is LaTeX-only; the GitHub README build takes plain pipe tables.
latex_out <- knitr::is_latex_output()

# kableExtra's styling verbs emit LaTeX and have no meaning under gfm, where the
# same table renders as a pipe table. Each call site says what LaTeX alone gets.
latex_only <- function(k, f) if (latex_out) f(k) else k
```

*Drafted by Claude Opus 5 under the supervision of Alex Coppock.*

This repository holds the actively maintained replication code for Coppock (2019), together with the reproducibility report that documents what the original archive did and did not do. It is part of a program applying the maintenance proposal in Peer, Orr and Coppock (2021, *PS: Political Science & Politics*, doi [10.1017/S1049096521000366](https://doi.org/10.1017/S1049096521000366)) to a set of published archives.

| | |
|---|---|
| Article | [10.1017/psrm.2018.10](https://doi.org/10.1017/psrm.2018.10) |
| Replication archive | [10.7910/DVN/F1CFFM](https://doi.org/10.7910/DVN/F1CFFM) |

**The data are not redistributed here.** The deposit is 38 files at Harvard Dataverse, which is the only copy this repository points at. `download_original.R` fetches it and verifies every file; `original_manifest.csv` pins the file identifiers, sizes and checksums, so the exact bytes this code was written against are recorded in version control even though the bytes themselves are not.

**Repository layout.** `maintained/` is the maintained rewrite: one script per published table or figure, writing to `output/`, which is committed so a reader can compare a fresh run against it without downloading anything, plus `in_text_claims.R`, which recomputes every number the article states in prose. `ground_truth/` ties every published number to the code that produces it: `published_claims.csv` is the extraction of the article, `build_ground_truth.R` builds the comparison and gates the pipeline on it. `original/` is created by the download script and is deliberately absent from the repository. This README is the reproducibility report, also available as a PDF in `report/`. `coppock_2019a_errata.pdf` corrects `r n_errata_word` sentences of the published article.

**License.** CC0 1.0 Universal, matching the terms of the deposit this repository maintains. See `LICENSE`.

**To reproduce.** Clone or download the repository, open `coppock_2019a.Rproj`, and run:

``` r
source("run_all.R")
```

That fetches the deposit, verifies its 38 files, and produces every table and figure into `maintained/output/`. Required packages: tidyverse, sandwich, lmtest, estimatr, metap, knitr, kableExtra, here. `metap` depends on `multtest` from Bioconductor, so it needs `BiocManager::install("multtest")` before `install.packages("metap")`. Paths resolve through `here`, so nothing depends on the working directory. A full run takes about a minute, most of it `table_2_ri_heterogeneity.R` recomputing 90 randomization inference tests. A successful run overwrites `maintained/output/`, which is committed: **`git diff` on that folder is the reproduction check.**

# Paper overview

**Citation**: Coppock, A. (2019). "Generalizing from Survey Experiments Conducted on Mechanical Turk: A Replication Approach." *Political Science Research and Methods*, 7(3), 613-628. DOI: 10.1017/psrm.2018.10

**Replication archive**: <https://doi.org/10.7910/DVN/F1CFFM>

**Summary**: The paper asks whether average treatment effects estimated on Mechanical Turk generalize to national probability samples. Fifteen survey experiments, originally fielded on probability or convenience samples, were replicated on MTurk, and seven were replicated a second time on TESS/GfK national probability samples. Treatments are framing, priming and information manipulations; outcomes are attitudes, standardized by the control group standard deviation in the original study. Effects are estimated by difference in means with Neyman (HC2) standard errors. Across 40 treatment-versus-control comparisons the MTurk and original estimates correlate at 0.85, and a randomization inference test of the null of treatment effect homogeneity rarely rejects, which is the mechanism the paper offers for why the samples agree.

---

# Summary

```{r summary_setup, include=FALSE}
# value_paper is forced to character in every reader: a column whose entries all look
# numeric is guessed as double, and that silently turns the article's 0.90 into 0.9 and
# 0.000 into 0, destroying the printed precision the comparison depends on.
gt_all <- read_csv(here("ground_truth", "coppock_2019a_ground_truth.csv"),
                   col_types = cols(.default = col_guess(),
                                    value_paper = col_character()))
claims <- read_csv(here("ground_truth", "published_claims.csv"),
                   col_types = cols(.default = col_character(),
                                    value_paper = col_character()))

n_claims <- nrow(gt_all)
n_rewrite_comparable <- sum(!is.na(gt_all$match_rewrite))
n_rewrite_match <- sum(gt_all$match_rewrite == 1, na.rm = TRUE)
n_rewrite_miss <- sum(gt_all$match_rewrite == 0, na.rm = TRUE)
n_script_comparable <- sum(!is.na(gt_all$match))
n_script_match <- sum(gt_all$match == 1, na.rm = TRUE)
n_extraction <- nrow(claims)
n_blocks <- sum(claims$needs_block == "TRUE")
miss_claims <- gt_all |> filter(match_rewrite == 0) |> pull(claim)

published_a1 <- read_csv(here("ground_truth", "published_table_a1.csv"),
                         col_types = cols(.default = col_character()))
published_appendix <- read_csv(here("ground_truth", "published_appendix_tables.csv"),
                               col_types = cols(.default = col_character()))
n_a1_cells <- nrow(published_a1)
n_appendix_cells <- 2 * nrow(published_appendix)
```

Two questions, answered before the detail.

## Does the deposited archive run?

Not as deposited, and the reasons split cleanly into the trivial and the substantive.

The trivial ones are two absent packages and a systematic path error. `metap`, used to combine p-values by Fisher's method, is not installed by default and pulls `multtest` from Bioconductor. `commarobust`, which supplies every standard error in the paper, was never on CRAN and now cannot be installed in working form at all; that one is treated below, because it has outgrown the trivial category. The path error is that eight `load()` calls name files ending `.rdata` when the deposited files end `.RData`. macOS does not care and Linux does, so six of the archive's seven scripts fail on their first data load on any case-sensitive filesystem. Nothing about the analysis is wrong; the archive simply cannot start.

The substantive ones are three.

First, two mistyped `sink()` calls silently destroyed two of the archive's own outputs. At line 249 of `coppock_generalizability_appendix.R`, a `sink()` naming Table 1's file stands where a bare `sink()` was meant, so instead of closing the Table 6 sink it reopens Table 1's file and truncates it: the deposited `..._table_1.txt` is zero bytes. At line 566 the same script writes Table 15's results to `..._table_5.txt`, overwriting the Patriot Act table that belongs there. The deposited `..._table_5.txt` contains the terrorism spending results, and no `..._table_15.txt` exists. Both errors are silent, and both survived into the published deposit.

Second, the uncorrected counts in Table 2 do not come back. The cause is not a bug in the archive but the change R 3.6.0 made to `sample()`, which replaced the rounding sampler with the rejection sampler and so changed which permutations a given seed draws. Setting `RNGkind(sample.kind = "Rounding")` and rerunning reproduces the deposited output exactly, 2 and 9 and 1 across the three samples, where the current sampler gives 1 and 8 and 1. The archive is reproducible; it is reproducible under the R of 2018.

Third, and separately from anything R did, the published Table 2's N Significant column is transposed. The deposited output file prints its three rows in alphabetical order of the sample name, TESS/GfK first and original last, and the published table prints them in the reverse order, original first. Table 2's N Comparisons column was reordered to match, 40 and 40 and 10; its N Significant column was not, so the published 1 in the Original row is the TESS/GfK count and the published 2 in the TESS/GfK row is the original count. The correct entries in the published row order are 2, 9 and 1, which is exactly what the deposit produces. The Holm-corrected column, which is the one the argument rests on, is symmetric under the same interchange and reproduces exactly under both samplers.

Fourth, the article's two power figures are not the ones its own simulation gives. The section is treated below and in the errata.

## Does the maintained rewrite reproduce the paper?

For `r n_rewrite_match` of the `r n_rewrite_comparable` comparable claims, yes. The correlations that carry the paper's argument reproduce to the reported precision (0.85, 0.90, 0.96, 0.85), as does the 72.5 percent replication rate. All `r n_a1_cells` published Table A1 entries reproduce, each an estimate, a standard error and a significance star; so do all `r n_appendix_cells` treatment estimate and standard error cells printed across the seventeen online appendix regression tables.

The `r n_rewrite_miss` claims that do not match fall into three groups. Two are the uncorrected significant-test counts for MTurk and TESS/GfK in Table 2, which are sampler-dependent for the reasons above; the rewrite reports what current R produces rather than reproducing the 2018 draw, because pinning a deprecated sampler to recover a specific integer would document the number rather than the finding. Two more are the power figures the article quotes from Figure 4, which its own deposited simulation contradicts. The last two are the sentence stating that no TESS/GfK test was significant, where the deposit says one was, and the sentence saying the analysis is limited to two dependent variables per study, which holds or fails depending on what counts as a study.

The substantive claim, that these tests rarely reject the null of treatment effect homogeneity, holds in every version: at most 9 of 40 comparisons reject before correction and at most 8 after.

---

# Original archive reproducibility

```{r repro_table}
tibble(
  Script = c(
    "coppock_generalizability_ri_functions.R",
    "coppock_generalizability_analysis.R",
    "coppock_generalizability_figures.R",
    "coppock_generalizability_table.R",
    "coppock_generalizability_ri_analysis.R",
    "coppock_generalizability_simulation.R",
    "coppock_generalizability_appendix.R"
  ),
  Status = c(
    "Clean (sourced by others; defines no paths)",
    "Fails on load(); fails again on commarobust",
    "Fails on load()",
    "Fails on load()",
    "Fails on load(); fails again on metap and commarobust",
    "Fails on load()",
    "Fails on load(); writes two outputs to the wrong file"
  ),
  Resolution = c(
    "No changes required",
    "Correct the filename case; inline the retired commarobust call",
    "Correct the filename case",
    "Correct the filename case",
    "Correct the filename case; install multtest and metap",
    "Correct the filename case",
    "Correct the filename case; correct two sink() calls"
  )
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Script", "Status on current R", "Resolution"),
    caption = "Original archive reproducibility, checked against R 4.6.0 on a case-sensitive reading of the deposited filenames."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 7) |>
    column_spec(1, width = "4cm") |>
    column_spec(2, width = "4cm") |>
    column_spec(3, width = "5cm"))
```

## Filename case

Every deposited data file ends `.RData`. Every script asks for `.rdata`:

```{r case_table}
tibble(
  Script = c(
    "coppock_generalizability_analysis.R:20",
    "coppock_generalizability_figures.R:21",
    "coppock_generalizability_figures.R:22",
    "coppock_generalizability_table.R:22",
    "coppock_generalizability_table.R:23",
    "coppock_generalizability_ri_analysis.R:20",
    "coppock_generalizability_appendix.R:20",
    "coppock_generalizability_simulation.R:60"
  ),
  Requested = c(
    "coppock_generalizability_studies.rdata",
    "coppock_generalizability_analysis_results.rdata",
    "coppock_generalizability_study_data.rdata",
    "coppock_generalizability_analysis_results.rdata",
    "coppock_generalizability_study_data.rdata",
    "coppock_generalizability_studies.rdata",
    "coppock_generalizability_studies.rdata",
    "coppock_generalizability_simulation_results.rdata"
  )
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Call site", "Filename requested"),
    caption = "The eight load() calls whose case does not match the deposited files. Each deposited counterpart ends .RData."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 7.5) |>
    column_spec(1, width = "6cm") |>
    column_spec(2, width = "7cm"))
```

The same defect had propagated into the maintained rewrite, whose six `load()` calls were copied from the archive. They are corrected here.

## The archive writes into itself

Six of the archive's scripts write their outputs into the archive directory, and five of those outputs are themselves deposited files. Running the deposit in place therefore overwrites part of the deposit: `coppock_generalizability_analysis_results.RData`, the three figure PDFs, and `coppock_generalizability_table_2.txt` all change. A seventh file, `ri_results.rdata`, is created and is not part of the deposit at all. Rerunning `download_original.R` restores everything, which is the reason the manifest records checksums rather than trusting whatever happens to be on disk.

## The standard error package no longer exists

Every estimate in the paper passes through `commarobust::commarobust_tidy()`. `commarobust` was never on CRAN. Its author retired it in November 2018 in favour of `estimatr`; the current GitHub head contains one function, a startup message reading "the commarobust package has been entirely replaced by the estimatr package", and exports nothing. Installing it from the default branch and calling `commarobust::commarobust` raises "not an exported object". The last working code sits on a branch named `legacy`.

An archive whose standard errors depend on an unversioned GitHub branch is exposed to a decision nobody in this project controls, so the rewrite does not depend on it. The retired `commarobust(fit)` was exactly

``` r
lmtest::coeftest(fit, sandwich::vcovHC(fit, type = "HC2"))
```

which is what `estimatr::lm_robust()` computes by default: HC2 is both its default variance estimator and the Neyman variance the paper reports. Every model in `maintained/analysis_ate_estimates.R` is therefore fitted with `lm_robust()` directly, and no helper stands between the call site and the estimator. Reproduction is exact to floating point: across all 90 estimates the largest disagreement with the values the archive's own package produced is 1.4e-12 in the point estimates and 8.0e-14 in the standard errors.

---

# Number-by-number comparison

```{r gt_table}
gt <- read_csv(
  here("ground_truth", "coppock_2019a_ground_truth.csv"),
  col_types = cols(.default = col_guess(), value_paper = col_character())
)

gt |>
  select(table_figure, claim, value_paper, value_script, match) |>
  kable(
    booktabs = TRUE,
    col.names = c("Location", "Quantity", "Paper", "Script", "Match"),
    caption = paste0("Ground truth: ", nrow(gt), " rows, comparing the published value to the deposit's own committed output."),
    digits = 4
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 6.5) |>
    column_spec(2, width = "6.5cm"))
```

`r n_script_match` of the `r n_script_comparable` published values with an archive counterpart are reproduced by the deposit's own committed output. `value_script` is read out of the objects and text files the archive itself deposited rather than typed or produced by re-running anything, and it is blank where the deposit prints nothing: Table 1's sample sizes, and the online appendix regression tables, whose deposited text files include two the archive's own mistyped `sink()` calls destroyed.

## Table 2 in full

```{r table2_compare}
tibble(
  cell = c("Original, uncorrected", "Mechanical Turk, uncorrected", "TESS/GfK, uncorrected",
           "Original, Holm", "Mechanical Turk, Holm", "TESS/GfK, Holm"),
  published_table = c(1, 9, 2, 0, 8, 0),
  published_text = c("1", "8", "0", "", "", "0"),
  deposited_output = c(2, 9, 1, 0, 8, 0),
  rounding_2026 = c(2, 9, 1, 0, 8, 0),
  current_2026 = c(1, 8, 1, 0, 8, 0)
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Cell", "Table 2", "Body text", "Deposited output", "Rounding sampler, 2026", "Current sampler, 2026"),
    caption = "Table 2's counts of significant homogeneity tests, from five sources. 'Deposited output' is the archive's own table 2 text file as it sits in the deposit. 'Rounding sampler' restores the pre-R-3.6.0 behaviour of the sampler behind sample()."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 7.5))
```

Three things follow. The archive is internally reproducible: the rounding sampler recovers the deposited output in every cell. The R 3.6.0 sampler change moves two cells, the MTurk and original counts, because one test in each of those samples has a maximum p-value of exactly 0.05 under the 2018 draw and none does under the current one.

And the published table's N Significant column is the deposited column in the deposited file's own row order. That file prints its rows alphabetically, `gfk` then `mt` then `original`, and reads 1, 9, 2 down the column. The published table prints its rows in the reverse order, Original then Mechanical Turk then TESS/GfK, and its N Significant column also reads 1, 9, 2. The N Comparisons column beside it was reordered correctly, 40 and 40 and 10 rather than 10 and 40 and 40, which is why the interchange is invisible from inside the table. The Holm column is symmetric under it and so cannot show it either. Under this reading every cell of the published table is accounted for: the correct entries in the published row order are 2, 9 and 1.

The alternative, that Table 2 was typeset from a run other than the one deposited, does not survive measurement. `ground_truth/measure_table_2_dispersion.R` runs the deposited procedure over a range of seeds under both samplers and records what it gets:

```{r dispersion_table}
dispersion <- read_csv(here("ground_truth", "table_2_seed_dispersion.csv"),
                       show_col_types = FALSE)

n_runs <- n_distinct(paste(dispersion$sampler, dispersion$seed))
gfk_range <- range(dispersion$n_sig[dispersion$sample == "gfk"])

dispersion |>
  summarise(
    runs = n(),
    counts = str_c(sort(unique(n_sig)), collapse = ", "),
    .by = c(sample, sampler)
  ) |>
  arrange(sample, sampler) |>
  kable(
    booktabs = TRUE,
    col.names = c("Sample", "Sampler", "Runs", "N Significant, values taken"),
    caption = paste0("Counts of significant homogeneity tests across ", n_runs,
                     " runs of the deposited procedure at different seeds.")
  ) |>
  latex_only(\(k) k |> kable_styling(latex_options = "hold_position"))
```

The TESS/GfK count was `r gfk_range[1]` in every one of the `r n_runs` runs and never `r as.numeric(claims$value_paper[claims$claim_id == "t2_gfk_n_sig"])`, while the original and MTurk counts both moved. A published TESS/GfK count of `r as.numeric(claims$value_paper[claims$claim_id == "t2_gfk_n_sig"])` is not something the deposited code produces.

The body text is a separate matter and is not settled by any of this. It reads 1, 8 and 0 where the deposit reads 2, 9 and 1. Its first two figures are the counts a strict `<` 0.05 would give on the deposit's own draw, where Table 2's own rule is `<=`, so the sentence and the table can differ legitimately by one in each of those samples. Its third figure has no such account: the TESS/GfK count is 1 under either rule and under either sampler. That sentence is corrected in `coppock_2019a_errata.pdf`; the other two are recorded as unresolved.

---

# Maintained rewrite

`maintained/` holds eight scripts and a shared `helpers.R`, replacing the archive's six analysis scripts and its function file. The rewrite is a translation: estimators, specifications and sample restrictions are unchanged.

```{r scripts_table}
tibble(
  Script = c(
    "helpers.R",
    "analysis_ate_estimates.R",
    "table_a1_ate_summary.R",
    "table_2_ri_heterogeneity.R",
    "figure_2_study_estimates.R",
    "figure_3_mt_original_scatter.R",
    "figure_4_power_simulation.R",
    "text_correlations.R",
    "in_text_claims.R"
  ),
  Output = c(
    "packages; Table A1 cell formatter",
    "output/analysis_results.rds",
    "output/table_a1_ate_summary.csv, .tex",
    "output/table_2_ri_heterogeneity.csv, .tex, output/ri_results.rds",
    "output/figure_2_study_estimates.csv, .pdf, .png",
    "output/figure_3_mt_original_scatter.csv, .pdf, .png",
    "output/figure_4_power_simulation.csv, .pdf, .png",
    "output/text_correlations.csv",
    "printed CLAIM lines only"
  )
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Script", "Output"),
    caption = "Maintained rewrite script inventory."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 8) |>
    column_spec(1, width = "5cm") |>
    column_spec(2, width = "8cm"))
```

## Deprecated patterns replaced

```{r replacements_table}
tibble(
  Original = c(
    "`rm(list = ls())`",
    "`setwd(\\\"\\\")`",
    "`load(\\\"...rdata\\\")` against a `.RData` file",
    "`commarobust::commarobust_tidy()`",
    "`do(...$summary_df)`",
    "`spread()` / `gather()`",
    "`geom_errorbarh()`",
    "`ggstance::position_dodgev()`",
    "`reshape2::melt()`",
    "`sink()` to a hardcoded path",
    "magrittr pipes"
  ),
  Replacement = c(
    "(omitted)",
    "`here::here()`",
    "the deposited filename, exact case",
    "`estimatr::lm_robust()`, whose default is HC2",
    "`reframe(...)` with `pick(everything())`",
    "`pivot_wider()` / `pivot_longer()`",
    "`geom_linerange()`",
    "`position_dodge(width = 0.5)`",
    "(the archive's saved result is read directly)",
    "`write_csv()` and `readr::write_lines()` to `output/`",
    "the native pipe"
  )
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Original pattern", "Replacement"),
    caption = "Deprecated patterns and their replacements in the maintained rewrite."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 8) |>
    column_spec(1, width = "6cm") |>
    column_spec(2, width = "7cm"))
```

## What the rewrite does not cover

The archive's `coppock_generalizability_appendix.R` produces the seventeen per-study regression tables of the online appendix. Each prints the same treatment coefficients the rewrite estimates, to three decimal places rather than Table A1's two, and every one of those `r n_appendix_cells` cells reproduces. Each table also prints an intercept, a sample size and an R-squared, and appendix Table 6 prints a party identification covariate. The rewrite drops the intercept and that covariate before writing its estimates and exports neither sample sizes nor R-squared, so those cells have no counterpart in `maintained/output/`; the ground truth records them as uncovered rather than as reproduced. Table 1's sample size columns are uncovered for the same reason.

Figure 1 is uncovered by anything. It illustrates the theoretical argument with a simulated population, and no script in the deposit draws it.

The rewrite also does not re-run the power simulation behind Figure 4. Neither does the archive: the simulation is commented out in `coppock_generalizability_simulation.R`, with a note that it "takes a *very* long time to run", and the deposited result object is loaded instead. The figure is reproduced from that object, and `figure_4_power_simulation.R` now writes the plotted grid to a CSV so the numbers the text quotes from it have a source.

## The power sentence

The article says of Figure 4 that at 500 subjects per treatment arm "we would be well powered (power $\approx$ 0.8) to detect treatment effect heterogeneity on the scale of 0.2 SD, and moderately powered for 0.1 SD (power $\approx$ 0.6)."

```{r power_table}
power <- read_csv(here("maintained", "output", "figure_4_power_simulation.csv"),
                  show_col_types = FALSE)

power_at <- function(sd) {
  value <- power$power[power$n_per_arm == 500 & power$sd_tau == sd]
  stopifnot(length(value) == 1)
  value
}

arm_for_08 <- min(power$n_per_arm[power$sd_tau == 0.2 & power$power >= 0.8])

tibble(
  scale = c("0.2 SD", "0.1 SD"),
  published = c(claims$value_paper[claims$claim_id == "fig4_power_at_02"],
                claims$value_paper[claims$claim_id == "fig4_power_at_01"]),
  simulated = sprintf("%.2f", c(power_at(0.2), power_at(0.1)))
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Heterogeneity scale", "Power stated in the text", "Power in the deposited simulation"),
    caption = "The two power figures the article quotes, against the simulation results it deposits, both at 500 subjects per treatment arm."
  ) |>
  latex_only(\(k) k |> kable_styling(latex_options = "hold_position"))
```

Figure 4 draws a dashed guide line at 500 subjects and another at power 0.8, and annotates the 0.2 SD curve where it crosses the second of them. The curve first reaches 0.8 at `r arm_for_08` subjects per arm, not 500, so the sentence reads the height of the guide line rather than the curve. The figure is right; the sentence is not, and it is corrected in `coppock_2019a_errata.pdf`. The claim the paper rests on, that the tests are powered against politically meaningful heterogeneity, survives at 0.2 SD and is weaker at 0.1 SD than the text says.

## Determinism

`table_2_ri_heterogeneity.R` sets the archive's seed once and recomputes all 90 tests on every run rather than reading back a cached result. Two independent runs, five months apart on different R versions, agree in every one of the 90 p-values to the last bit. The 90 tests take a minute. The script deliberately does not skip its work when `output/ri_results.rds` already exists: a script that does that cannot be checked by diffing its own output, which is what this repository asks a reader to do.

---

# Figures

```{r fig2, fig.cap="Figure 2: standardized ATE estimates by study and sample.", out.width="100%"}
knitr::include_graphics(
  here("maintained", "output",
       if (latex_out) "figure_2_study_estimates.pdf" else "figure_2_study_estimates.png")
)
```

```{r fig3, fig.cap="Figure 3: MTurk versus original standardized estimates.", out.width="80%"}
knitr::include_graphics(
  here("maintained", "output",
       if (latex_out) "figure_3_mt_original_scatter.pdf" else "figure_3_mt_original_scatter.png")
)
```

```{r fig4, fig.cap="Figure 4: power of the homogeneity test by sample size and effect heterogeneity.", out.width="80%"}
knitr::include_graphics(
  here("maintained", "output",
       if (latex_out) "figure_4_power_simulation.pdf" else "figure_4_power_simulation.png")
)
```

---

# Tables

```{r tab2}
read_csv(here("maintained", "output", "table_2_ri_heterogeneity.csv"),
         show_col_types = FALSE) |>
  kable(
    booktabs = TRUE,
    col.names = c("Sample", "N comparisons", "N significant", "N significant (Holm)"),
    caption = "Table 2 as the maintained rewrite produces it."
  ) |>
  latex_only(\(k) k |> kable_styling(latex_options = "hold_position"))
```

```{r taba1}
read_csv(here("maintained", "output", "table_a1_ate_summary.csv"),
         show_col_types = FALSE) |>
  select(study_print, dv_name, coef_name, original_entry, mt_entry, gfk_entry) |>
  kable(
    booktabs = TRUE,
    col.names = c("Study", "Outcome", "Coefficient", "Original", "MTurk", "GfK"),
    caption = "Table A1 as the maintained rewrite produces it: standardized ATE estimates by study, outcome and sample, with HC2 standard errors in parentheses.",
    na = ""
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 6.5) |>
    column_spec(1, width = "3.5cm") |>
    column_spec(2, width = "3.5cm") |>
    column_spec(3, width = "3cm"))
```

---

# The extraction and the two instruments

Every published number in this article and its online appendix is written down once, in `ground_truth/published_claims.csv`. That file is the extraction: `r n_extraction` rows, each carrying a claim identifier, where the number appears, what kind of claim it is, the string the page prints and the number of decimals it prints it to. It is the only place in the repository a published number is typed, and nothing in `maintained/` reads it except for those decimal counts.

```{r extraction_table}
claims |>
  count(claim_type, needs_block) |>
  mutate(needs_block = if_else(needs_block == "TRUE", "yes", "no")) |>
  kable(
    booktabs = TRUE,
    col.names = c("Claim type", "Needs a claim block", "Claims"),
    caption = paste0("The extraction: ", nrow(claims),
                     " published claims, classified by hand.")
  ) |>
  latex_only(\(k) k |> kable_styling(latex_options = "hold_position"))
```

A `pipeline` claim is one the analysis produces; `descriptive` claims are about shape, sign or count and have no printed number to compare; `definitional` and `structural` claims are design parameters and layout facts; `transcribed` claims are copied from other articles and cannot drift. The `needs_block` column is TRUE where the pipeline can print something true about the claim, which is `r n_blocks` of the `r n_extraction`. The remainder are verified where they are used: the confidence level of the plausible-effects interval is visible in the `qnorm(0.9999)` call the archive's own function file makes, Figure 4's guide lines in the `geom_hline()` and `geom_vline()` that draw them, and the significance threshold behind Table A1's stars in `helpers.R`.

Two separate instruments then check the same claims.

`ground_truth/build_ground_truth.R` assembles the comparison table. It reads `value_rewrite` back out of `maintained/output/` and `value_script` out of the objects and text files the archive deposited, so neither column can drift from what it describes, and it compares each against the published string by printing the computed number to the page's own precision rather than by a numeric tolerance, because a double does not record how many decimals the article printed.

`maintained/in_text_claims.R` carries one block per claim needing one: the article's sentence verbatim in a comment, then code that recomputes the number from the same committed outputs by its own path. It never reads the ground truth. The two reach the same quantities differently, so a disagreement between them is a finding rather than a formality: the ground truth reads the correlations out of `text_correlations.csv` while the claims file rebuilds them from the estimates.

The build script is the gate. It runs `in_text_claims.R` non-interactively into its own environment, counts the `CLAIM` lines it printed, and stops unless that count equals the `r n_blocks` claims the extraction says need one, every identifier appears on both sides, every `pipeline` and `descriptive` claim has a ground truth row, every published float has coverage or a stated reason, every adverse verdict carries a `defect_locus` and no clean match does, and the two instruments agree value by value. A block that errored, or that ended in a bare expression and so printed nothing, would satisfy a scan for markers while checking nothing, which is why the file is run rather than read.

`r str_to_sentence(n_errata_word)` sentences of the published article are corrected in `coppock_2019a_errata.pdf` at the root of this repository. Neither changes a conclusion.

# Maintained rewrite verification

```{r rewrite_verify}
gt |>
  select(table_figure, claim, value_paper, value_rewrite, match_rewrite) |>
  kable(
    booktabs = TRUE,
    col.names = c("Location", "Quantity", "Paper", "Rewrite", "Match"),
    caption = "Maintained rewrite verification: published value against rewrite output.",
    digits = 4
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 6.5) |>
    column_spec(2, width = "6.5cm"))
```

**`r n_rewrite_match`** of the **`r n_rewrite_comparable`** comparable claims match the published values. The `r n_rewrite_miss` that do not are discussed above: `r paste(miss_claims, collapse = "; ")`.

The rows with no `match_rewrite` are those the rewrite does not compute, and they are recorded rather than dropped: Table 1's sample sizes, the intercept, sample size and R-squared rows of the seventeen online appendix tables, and the article's claim about the typical number of subjects per treatment arm.

---

# R environment

```{r env}
si <- sessionInfo()
pkgs <- c("tidyverse", "sandwich", "lmtest", "estimatr", "metap", "knitr", "kableExtra", "here")

bind_rows(
  tibble(
    item = c("R version", "Platform", "Date run"),
    value = c(
      paste(si$R.version$major, si$R.version$minor, sep = "."),
      si$platform,
      format(Sys.Date())
    )
  ),
  tibble(item = pkgs, value = map_chr(pkgs, \(p) as.character(packageVersion(p))))
) |>
  kable(booktabs = TRUE, col.names = c("Item", "Value")) |>
  latex_only(\(k) k |> kable_styling(latex_options = "hold_position"))
```
