---
title: "Active Maintenance Report: coppock_2019a"
subtitle: "Coppock (2019, PSRM): Generalizing from Survey Experiments Conducted on Mechanical Turk"
format:
  gfm:
    output-file: README.md
    toc: true
  pdf:
    output-file: coppock_2019a_report.pdf
    toc: true
    toc-depth: 2
    number-sections: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)

here::i_am("README.qmd")

# kableExtra styling is LaTeX-only; the GitHub README build takes plain pipe tables.
latex_out <- knitr::is_latex_output()

# kableExtra's styling verbs emit LaTeX and have no meaning under gfm, where the
# same table renders as a pipe table. Each call site says what LaTeX alone gets.
latex_only <- function(k, f) if (latex_out) f(k) else k
```

This repository holds the actively maintained replication code for Coppock (2019), together with the reproducibility report that documents what the original archive did and did not do. It is part of a program applying the maintenance proposal in Peer, Orr and Coppock (2021, *PS: Political Science & Politics*, doi [10.1017/S1049096521000366](https://doi.org/10.1017/S1049096521000366)) to a set of published archives.

| | |
|---|---|
| Article | [10.1017/psrm.2018.10](https://doi.org/10.1017/psrm.2018.10) |
| Replication archive | [10.7910/DVN/F1CFFM](https://doi.org/10.7910/DVN/F1CFFM) |

**The data are not redistributed here.** The deposit is 38 files at Harvard Dataverse, which is the only copy this repository points at. `download_original.R` fetches it and verifies every file; `original_manifest.csv` pins the file identifiers, sizes and checksums, so the exact bytes this code was written against are recorded in version control even though the bytes themselves are not.

**Repository layout.** `maintained/` is the maintained rewrite: one script per published table or figure, writing to `output/`, which is committed so a reader can compare a fresh run against it without downloading anything. `ground_truth/` ties every published number to the code that produces it. `original/` is created by the download script and is deliberately absent from the repository. This README is the reproducibility report, also available as a PDF in `report/`.

**License.** CC0 1.0 Universal, matching the terms of the deposit this repository maintains. See `LICENSE`.

**To reproduce.** Clone or download the repository, open `coppock_2019a.Rproj`, and run:

``` r
source("run_all.R")
```

That fetches the deposit, verifies its 38 files, and produces every table and figure into `maintained/output/`. Required packages: tidyverse, sandwich, lmtest, estimatr, metap, knitr, kableExtra, here. `metap` depends on `multtest` from Bioconductor, so it needs `BiocManager::install("multtest")` before `install.packages("metap")`. Paths resolve through `here`, so nothing depends on the working directory. A full run takes about a minute, most of it `table_2_ri_heterogeneity.R` recomputing 90 randomization inference tests. A successful run overwrites `maintained/output/`, which is committed: **`git diff` on that folder is the reproduction check.**

# Paper overview

**Citation**: Coppock, A. (2019). "Generalizing from Survey Experiments Conducted on Mechanical Turk: A Replication Approach." *Political Science Research and Methods*, 7(3), 613-628. DOI: 10.1017/psrm.2018.10

**Replication archive**: <https://doi.org/10.7910/DVN/F1CFFM>

**Summary**: The paper asks whether average treatment effects estimated on Mechanical Turk generalize to national probability samples. Fifteen survey experiments, originally fielded on probability or convenience samples, were replicated on MTurk, and seven were replicated a second time on TESS/GfK national probability samples. Treatments are framing, priming and information manipulations; outcomes are attitudes, standardized by the control group standard deviation in the original study. Effects are estimated by difference in means with Neyman (HC2) standard errors. Across 40 treatment-versus-control comparisons the MTurk and original estimates correlate at 0.85, and a randomization inference test of the null of treatment effect homogeneity rarely rejects, which is the mechanism the paper offers for why the samples agree.

---

# Summary

```{r summary_setup, include=FALSE}
gt_all <- read_csv(here("ground_truth", "coppock_2019a_ground_truth.csv"),
                   show_col_types = FALSE)
n_claims <- nrow(gt_all)
n_rewrite_match <- sum(gt_all$match_rewrite == 1, na.rm = TRUE)
n_rewrite_miss <- sum(gt_all$match_rewrite == 0, na.rm = TRUE)
n_script_match <- sum(gt_all$match == 1, na.rm = TRUE)
miss_claims <- gt_all |> filter(match_rewrite == 0) |> pull(claim)
```

Two questions, answered before the detail.

## Does the deposited archive run?

Not as deposited, and the reasons split cleanly into the trivial and the substantive.

The trivial ones are two absent packages and a systematic path error. `metap`, used to combine p-values by Fisher's method, is not installed by default and pulls `multtest` from Bioconductor. `commarobust`, which supplies every standard error in the paper, was never on CRAN and now cannot be installed in working form at all; that one is treated below, because it has outgrown the trivial category. The path error is that eight `load()` calls name files ending `.rdata` when the deposited files end `.RData`. macOS does not care and Linux does, so six of the archive's seven scripts fail on their first data load on any case-sensitive filesystem. Nothing about the analysis is wrong; the archive simply cannot start.

The substantive ones are three.

First, two mistyped `sink()` calls silently destroyed two of the archive's own outputs. At line 249 of `coppock_generalizability_appendix.R`, a `sink()` naming Table 1's file stands where a bare `sink()` was meant, so instead of closing the Table 6 sink it reopens Table 1's file and truncates it: the deposited `..._table_1.txt` is zero bytes. At line 566 the same script writes Table 15's results to `..._table_5.txt`, overwriting the Patriot Act table that belongs there. The deposited `..._table_5.txt` contains the terrorism spending results, and no `..._table_15.txt` exists. Both errors are silent, and both survived into the published deposit.

Second, the uncorrected counts in Table 2 do not come back. The cause is not a bug in the archive but the change R 3.6.0 made to `sample()`, which replaced the rounding sampler with the rejection sampler and so changed which permutations a given seed draws. Setting `RNGkind(sample.kind = "Rounding")` and rerunning reproduces the deposited output exactly, 2 and 9 and 1 across the three samples, where the current sampler gives 1 and 8 and 1. The archive is reproducible; it is reproducible under the R of 2018.

Third, and separately from anything R did, the published Table 2 disagrees with the paper's own text and with the archive. Table 2 reports 1, 9 and 2 significant tests for the original, MTurk and TESS/GfK samples; the text on the facing page says 1, 8 and 0. The archive produces 2, 9 and 1 as deposited. No single run of the code produces the published column. The Holm-corrected column, which is the one the argument rests on, reproduces exactly under both samplers.

## Does the maintained rewrite reproduce the paper?

For `r n_rewrite_match` of `r n_claims` recorded claims, yes. The correlations that carry the paper's argument reproduce to the reported precision (0.85, 0.90, 0.96, 0.85), as do the 72.5 percent replication rate, every checked Table A1 estimate, and every cell of Table 2 except two.

The `r n_rewrite_miss` that do not match are the uncorrected significant-test counts for MTurk and TESS/GfK in Table 2, for the reasons above: they are sampler-dependent, and the published values are not reproducible from the archive under any sampler. The rewrite reports what current R produces rather than reproducing the 2018 draw, because pinning a deprecated sampler to recover a specific integer would document the number rather than the finding. The substantive claim, that these tests rarely reject the null of treatment effect homogeneity, holds in every version: at most 9 of 40 comparisons reject before correction and at most 8 after.

---

# Original archive reproducibility

```{r repro_table}
tibble(
  Script = c(
    "coppock_generalizability_ri_functions.R",
    "coppock_generalizability_analysis.R",
    "coppock_generalizability_figures.R",
    "coppock_generalizability_table.R",
    "coppock_generalizability_ri_analysis.R",
    "coppock_generalizability_simulation.R",
    "coppock_generalizability_appendix.R"
  ),
  Status = c(
    "Clean (sourced by others; defines no paths)",
    "Fails on load(); fails again on commarobust",
    "Fails on load()",
    "Fails on load()",
    "Fails on load(); fails again on metap and commarobust",
    "Fails on load()",
    "Fails on load(); writes two outputs to the wrong file"
  ),
  Resolution = c(
    "No changes required",
    "Correct the filename case; inline the retired commarobust call",
    "Correct the filename case",
    "Correct the filename case",
    "Correct the filename case; install multtest and metap",
    "Correct the filename case",
    "Correct the filename case; correct two sink() calls"
  )
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Script", "Status on current R", "Resolution"),
    caption = "Original archive reproducibility, checked against R 4.6.0 on a case-sensitive reading of the deposited filenames."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 7) |>
    column_spec(1, width = "4cm") |>
    column_spec(2, width = "4cm") |>
    column_spec(3, width = "5cm"))
```

## Filename case

Every deposited data file ends `.RData`. Every script asks for `.rdata`:

```{r case_table}
tibble(
  Script = c(
    "coppock_generalizability_analysis.R:20",
    "coppock_generalizability_figures.R:21",
    "coppock_generalizability_figures.R:22",
    "coppock_generalizability_table.R:22",
    "coppock_generalizability_table.R:23",
    "coppock_generalizability_ri_analysis.R:20",
    "coppock_generalizability_appendix.R:20",
    "coppock_generalizability_simulation.R:60"
  ),
  Requested = c(
    "coppock_generalizability_studies.rdata",
    "coppock_generalizability_analysis_results.rdata",
    "coppock_generalizability_study_data.rdata",
    "coppock_generalizability_analysis_results.rdata",
    "coppock_generalizability_study_data.rdata",
    "coppock_generalizability_studies.rdata",
    "coppock_generalizability_studies.rdata",
    "coppock_generalizability_simulation_results.rdata"
  )
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Call site", "Filename requested"),
    caption = "The eight load() calls whose case does not match the deposited files. Each deposited counterpart ends .RData."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 7.5) |>
    column_spec(1, width = "6cm") |>
    column_spec(2, width = "7cm"))
```

The same defect had propagated into the maintained rewrite, whose six `load()` calls were copied from the archive. They are corrected here.

## The archive writes into itself

Six of the archive's scripts write their outputs into the archive directory, and five of those outputs are themselves deposited files. Running the deposit in place therefore overwrites part of the deposit: `coppock_generalizability_analysis_results.RData`, the three figure PDFs, and `coppock_generalizability_table_2.txt` all change. A seventh file, `ri_results.rdata`, is created and is not part of the deposit at all. Rerunning `download_original.R` restores everything, which is the reason the manifest records checksums rather than trusting whatever happens to be on disk.

## The standard error package no longer exists

Every estimate in the paper passes through `commarobust::commarobust_tidy()`. `commarobust` was never on CRAN. Its author retired it in November 2018 in favour of `estimatr`; the current GitHub head contains one function, a startup message reading "the commarobust package has been entirely replaced by the estimatr package", and exports nothing. Installing it from the default branch and calling `commarobust::commarobust` raises "not an exported object". The last working code sits on a branch named `legacy`.

An archive whose standard errors depend on an unversioned GitHub branch is exposed to a decision nobody in this project controls, so the rewrite does not depend on it. The retired `commarobust(fit)` was exactly

``` r
lmtest::coeftest(fit, sandwich::vcovHC(fit, type = "HC2"))
```

which is what `estimatr::lm_robust()` computes by default: HC2 is both its default variance estimator and the Neyman variance the paper reports. Every model in `maintained/analysis_ate_estimates.R` is therefore fitted with `lm_robust()` directly, and no helper stands between the call site and the estimator. Reproduction is exact to floating point: across all 90 estimates the largest disagreement with the values the archive's own package produced is 1.4e-12 in the point estimates and 8.0e-14 in the standard errors.

---

# Number-by-number comparison

```{r gt_table}
gt <- read_csv(
  here("ground_truth", "coppock_2019a_ground_truth.csv"),
  show_col_types = FALSE
)

gt |>
  select(table_figure, claim, value_paper, value_script, match) |>
  kable(
    booktabs = TRUE,
    col.names = c("Location", "Quantity", "Paper", "Script", "Match"),
    caption = paste0("Ground truth: ", nrow(gt), " rows, comparing the published value to a 2026 re-run of the deposited scripts."),
    digits = 4
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 6.5) |>
    column_spec(2, width = "6.5cm"))
```

`r n_script_match` of `r n_claims` published values are reproduced by a current re-run of the deposited scripts. The two exceptions are the uncorrected significant-test counts for MTurk and TESS/GfK in Table 2.

## Table 2 in full

```{r table2_compare}
tibble(
  cell = c("Original, uncorrected", "Mechanical Turk, uncorrected", "TESS/GfK, uncorrected",
           "Original, Holm", "Mechanical Turk, Holm", "TESS/GfK, Holm"),
  published_table = c(1, 9, 2, 0, 8, 0),
  published_text = c("1", "8", "0", "", "", "0"),
  deposited_output = c(2, 9, 1, 0, 8, 0),
  rounding_2026 = c(2, 9, 1, 0, 8, 0),
  current_2026 = c(1, 8, 1, 0, 8, 0)
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Cell", "Table 2", "Body text", "Deposited output", "Rounding sampler, 2026", "Current sampler, 2026"),
    caption = "Table 2's counts of significant homogeneity tests, from five sources. 'Deposited output' is the archive's own table 2 text file as it sits in the deposit. 'Rounding sampler' restores the pre-R-3.6.0 behaviour of the sampler behind sample()."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 7.5))
```

Three things follow. The archive is internally reproducible: the rounding sampler recovers the deposited output in every cell. The R 3.6.0 sampler change moves two cells. The published table, meanwhile, matches no run of the code: its Original count agrees with the current sampler while its MTurk count agrees with the 2018 one, and its TESS/GfK count of 2 appears nowhere, in the archive or in the paper's own text.

The most likely explanation is that Table 2 was typeset from an earlier execution than the one deposited, which is a hazard specific to results whose value depends on a random draw and is only weakly pinned by a seed. With `sims = 100` a p-value is a multiple of 0.01, and a count of how many of 90 such p-values fall at or below 0.05 will move by one or two between runs.

---

# Maintained rewrite

`maintained/` holds seven scripts and a shared `helpers.R`, replacing the archive's six analysis scripts and its function file. The rewrite is a translation: estimators, specifications and sample restrictions are unchanged.

```{r scripts_table}
tibble(
  Script = c(
    "helpers.R",
    "analysis_ate_estimates.R",
    "table_a1_ate_summary.R",
    "table_2_ri_heterogeneity.R",
    "figure_2_study_estimates.R",
    "figure_3_mt_original_scatter.R",
    "figure_4_power_simulation.R",
    "text_correlations.R"
  ),
  Output = c(
    "packages; HC2 tidier; Table A1 cell formatter",
    "output/analysis_results.rds",
    "output/table_a1_ate_summary.csv, .tex",
    "output/table_2_ri_heterogeneity.csv, .tex, output/ri_results.rds",
    "output/figure_2_study_estimates.pdf, .png",
    "output/figure_3_mt_original_scatter.pdf, .png",
    "output/figure_4_power_simulation.pdf, .png",
    "output/text_correlations.csv"
  )
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Script", "Output"),
    caption = "Maintained rewrite script inventory."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 8) |>
    column_spec(1, width = "5cm") |>
    column_spec(2, width = "8cm"))
```

## Deprecated patterns replaced

```{r replacements_table}
tibble(
  Original = c(
    "`rm(list = ls())`",
    "`setwd(\\\"\\\")`",
    "`load(\\\"...rdata\\\")` against a `.RData` file",
    "`commarobust::commarobust_tidy()`",
    "`do(...$summary_df)`",
    "`spread()` / `gather()`",
    "`geom_errorbarh()`",
    "`ggstance::position_dodgev()`",
    "`reshape2::melt()`",
    "`sink()` to a hardcoded path",
    "magrittr pipes"
  ),
  Replacement = c(
    "(omitted)",
    "`here::here()`",
    "the deposited filename, exact case",
    "`estimatr::lm_robust()`, whose default is HC2",
    "`reframe(...)` with `pick(everything())`",
    "`pivot_wider()` / `pivot_longer()`",
    "`geom_linerange()`",
    "`position_dodge(width = 0.5)`",
    "(the archive's saved result is read directly)",
    "`write_csv()` and `readr::write_lines()` to `output/`",
    "the native pipe"
  )
) |>
  kable(
    booktabs = TRUE,
    col.names = c("Original pattern", "Replacement"),
    caption = "Deprecated patterns and their replacements in the maintained rewrite."
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 8) |>
    column_spec(1, width = "6cm") |>
    column_spec(2, width = "7cm"))
```

## What the rewrite does not cover

The archive's `coppock_generalizability_appendix.R` produces sixteen per-study regression tables for the online appendix. The rewrite does not reproduce them, and they are not represented in the ground truth. They are the natural next addition, and the two `sink()` errors documented above mean that two of them cannot be checked against the deposit at all.

The rewrite also does not re-run the power simulation behind Figure 4. Neither does the archive: the simulation is commented out in `coppock_generalizability_simulation.R`, with a note that it "takes a *very* long time to run", and the deposited result object is loaded instead. The figure is reproduced from that object.

## Determinism

`table_2_ri_heterogeneity.R` sets the archive's seed once and recomputes all 90 tests on every run rather than reading back a cached result. Two independent runs, five months apart on different R versions, agree in every one of the 90 p-values to the last bit. The 90 tests take a minute, not the half hour the March notes estimated without checking. The script deliberately does not skip its work when `output/ri_results.rds` already exists: a script that does that cannot be checked by diffing its own output, which is what this repository asks a reader to do.

---

# Figures

```{r fig2, fig.cap="Figure 2: standardized ATE estimates by study and sample.", out.width="100%"}
knitr::include_graphics(
  here("maintained", "output",
       if (latex_out) "figure_2_study_estimates.pdf" else "figure_2_study_estimates.png")
)
```

```{r fig3, fig.cap="Figure 3: MTurk versus original standardized estimates.", out.width="80%"}
knitr::include_graphics(
  here("maintained", "output",
       if (latex_out) "figure_3_mt_original_scatter.pdf" else "figure_3_mt_original_scatter.png")
)
```

```{r fig4, fig.cap="Figure 4: power of the homogeneity test by sample size and effect heterogeneity.", out.width="80%"}
knitr::include_graphics(
  here("maintained", "output",
       if (latex_out) "figure_4_power_simulation.pdf" else "figure_4_power_simulation.png")
)
```

---

# Tables

```{r tab2}
read_csv(here("maintained", "output", "table_2_ri_heterogeneity.csv"),
         show_col_types = FALSE) |>
  kable(
    booktabs = TRUE,
    col.names = c("Sample", "N comparisons", "N significant", "N significant (Holm)"),
    caption = "Table 2 as the maintained rewrite produces it."
  ) |>
  latex_only(\(k) k |> kable_styling(latex_options = "hold_position"))
```

```{r taba1}
read_csv(here("maintained", "output", "table_a1_ate_summary.csv"),
         show_col_types = FALSE) |>
  select(study_print, dv_name, coef_name, original_entry, mt_entry, gfk_entry) |>
  kable(
    booktabs = TRUE,
    col.names = c("Study", "Outcome", "Coefficient", "Original", "MTurk", "GfK"),
    caption = "Table A1 as the maintained rewrite produces it: standardized ATE estimates by study, outcome and sample, with HC2 standard errors in parentheses.",
    na = ""
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 6.5) |>
    column_spec(1, width = "3.5cm") |>
    column_spec(2, width = "3.5cm") |>
    column_spec(3, width = "3cm"))
```

---

# Maintained rewrite verification

```{r rewrite_verify}
gt |>
  select(table_figure, claim, value_paper, value_rewrite, match_rewrite) |>
  kable(
    booktabs = TRUE,
    col.names = c("Location", "Quantity", "Paper", "Rewrite", "Match"),
    caption = "Maintained rewrite verification: published value against rewrite output.",
    digits = 4
  ) |>
  latex_only(\(k) k |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 6.5) |>
    column_spec(2, width = "6.5cm"))
```

**`r n_rewrite_match`** of **`r n_claims`** claims match the published values. The `r n_rewrite_miss` that do not are `r paste(miss_claims, collapse = " and ")`, discussed above.

---

# R environment

```{r env}
si <- sessionInfo()
pkgs <- c("tidyverse", "sandwich", "lmtest", "estimatr", "metap", "knitr", "kableExtra", "here")

bind_rows(
  tibble(
    item = c("R version", "Platform", "Date run"),
    value = c(
      paste(si$R.version$major, si$R.version$minor, sep = "."),
      si$platform,
      format(Sys.Date())
    )
  ),
  tibble(item = pkgs, value = map_chr(pkgs, \(p) as.character(packageVersion(p))))
) |>
  kable(booktabs = TRUE, col.names = c("Item", "Value")) |>
  latex_only(\(k) k |> kable_styling(latex_options = "hold_position"))
```
